---
title: "Relational Data"
output: html_document
---

```{r}
library(tidyverse)
library(nycflights13)

weather

```
1. You would need to know the flights origin and destination. By combining the weather and airports tables you can obtain this information.
2. The weather and airports share origin. The weather table also contains year, month, day, and hour.  The airports table also contains destination.
3. The weather table would also need to contain the destination to know the weather for all airports in the USA.
4. Month, day, and hour would probably be most important for finding what days would be less travelled.


```{r}

flights %>% count(year, month, day, flight) %>% filter(n > 1)

```

```{r}

flights %>% mutate(surrogate = row_number())

```

2. a. Lahman  b. babynames  c. nasaweather  d. fueleconomy  e. ggplot2.

```{r}

library(Lahman)

Master | Batting | Salaries
---------------------------
Player Names | Batting Statistics | Player Salary Data
Dates of Birth |
Dates of Death |
Biographical Info |

```
3. The three tables use the same players but describe different data.


```{r}

flights2 <- flights %>%
  select(year:day, hour, origin, dest, tailnum, carrier)
flights2

```

```{r}

flights2 %>% select(-origin, -dest) %>%
  left_join(airlines, by = "carrier")

```

```{r}

x <- tribble(
  ~key, ~val_x,
    1, "x1",
    2, "x2",
    2, "x2",
    1, "x4"
  )
y <- tribble(
  ~key, ~val_y,
    1, "y1",
    2, "y2"
)
left_join(x, y, by = "key")

```


```{r}

flights2 %>%
  left_join(planes, by = "tailnum")

```

```{r}
flights %>%
  group_by(dest) %>% 
  summarize( avg = mean(flights)) %>%
  semi_join(airports, c("dest" = "faa")) %>%
  ggplot(aes(lon, lat)) +
    borders("state") +
    geom_point() +
    coord_quickmap()

```

```{r}



```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
